### 2020-10-07 paper/natastron/methods.tex
Tidied up separate documents

\section*{Methods}
\setcounter{tocdepth}{2}
\tableofcontents
\section{Asteroseismic Methods}
\subsection{Asteroseismic Data}
For our asteroseismic power spectrum data we used the unweighted power spectra from the KASOC pipeline \cite{handberg+lund2014}\footnote{Obtainable from the \href{http://kasoc.phys.au.dk/}{KASOC} webpage.}. We did not apply any additional treatment to these data. For 16 Cyg A \& B (KIC 12069424 and KIC 12069449) we used the KEPSEISMIC lightcurves \cite{garcia+2011}\footnote{Obtainable from \href{https://archive.
		stsci.edu/prepds/kepseismic/}{MAST}.}, which have significantly better signal-to-noise for these two stars.

For our asteroseismic ages, we used the ages obtained by \texttt{BASTA} \cite[BAyesian STellar Algorithm]{silvaaguirre+2015} in the `Kages' and LEGACY catalogues. These ages have been obtained by comparisons of measured oscillation properties to stellar models, accounting for an expanded range of metallicities. \texttt{BASTA} is thoroughly compared to four other seismic modelling techniques in \cite{silvaaguirre+2017}. While uncertainties found through \texttt{BASTA} are typically higher than for other techniques, only \texttt{BASTA} and \texttt{ASTFIT} \cite[Aarhus STellar Evolution Code]{christensen-dalsgaard2008} recover the radius, mass and age of the Sun, when applied to solar data. Although the uncertainties on \texttt{ASTFIT} ages are overall lower, they are not published for the `Kages' sample. In order to maintain an internally consistent stellar age sample, we used age results from \texttt{BASTA} for both the `Kages' and LEGACY samples.

@@

As described in the catalogue papers, for `Kages' stars atmospheric properties (\teff and \feh) were measured through high-resolution spectroscopy reported in \cite{huber+2013a}. For LEGACY stars, atmospheric properties were similarly taken from \cite{buchhave+latham2015} for most stars in the catalogue, and complemented by other values from the literature for the remaining stars \cite[see Table 3]{silvaaguirre+2017}.

Other asteroseismic properties used in this study, such as those used as first guesses on the free parameters in our asteroseismic model, were taken from the `Kages' and LEGACY catalogues \cite{astropycollaboration+2013, astropycollaboration+2018, ginsburg+2019}. In cases where both catalogues contained the same target, we used the stellar parameters reported in LEGACY \cite{mckinney2010}. This is also the case for the masses and ages described above.

@@

In order to extract signatures of stellar rotation from the asteroseismic mode frequencies, we built a model that simultaneously treats the convective background, modes of oscillation, and white noise, while accounting for rotational splitting. The foundations of this approach follows best-practices in asteroseismology \cite{davies+2015}, fitting Harvey profiles for the background \cite{harvey1985}, and expressing the frequencies of the modes using an asymptotic expression \cite{tassoul1980, vrard+2016}.

The first core improvement in this work come in the form of the use of hierarchical models, which account for small-scale deviations in mode frequencies due to effects not explicitly accounted for in our model (such as acoustic glitches \cite{mazumdar+2014}). By improving the inference of mode frequencies in this way, we also improve the ability to resolve the rotational splitting. The second improvement comes in the form of priors on our parameters, and in particular the rotational inclination, which more accurately reflects the true distribution of angles than previous techniques \cite{chaplin+basu2017}. A step-by-step breakdown of the model and all priors can be found in \textbf{Supplementary Materials}.\\

We separated our model fitting into two parts. First, we fit a model for the convective background and white noise only, to the region of the power spectra that did not contain modes of oscillation. This was done using \texttt{PyStan} \cite{vanhoey+2013,carpenter+2017}, for 10,000 iterations on each star\footnote{These \texttt{PyStan} runs were initiated with a random seed of 11, as were all other random processes in this work}. Second, we fit our full model (including the convective background) to the region containing the modes of oscillation. The results of the first fit to the convective background were used as extremely informative priors on the background parameters in this second fit. This was done using \texttt{PyMC3} \cite{vanderwalt+2011,salvatier+2016, thetheanodevelopmentteam+2016} for 2500 iterations each on 4 chains.

From this asteroseismic analysis, we report inclination angle ($i$), rotational splitting ($\nu_{\rm s}$), and rotation period ($P$) in \textbf{Extended Data} Table 1. The summary statistics on these parameters were taken as the median of the posterior distribution, with uncertainties being the $15.9^{\rm th}$ and $84.1^{\rm st}$ percentiles. For inclination angle ($i = \arccos(\cos(i))$) and rotation ($P = 1/\nu_{\rm s}$), the full posterior samples were transformed before taking the summary statistics, as our model sampled in $\cos(i)$ and $\nu_{\rm s}$.

We flagged any sub-optimal conditions of the final fit. Of 94 stars, we flagged 5 for which the Gelman-Rubin convergence metric, $\hat{R}$, was greater than 1.01 and 2 stars for which it was greater than 1.1 on inclination angle or rotation, where a $\hat{R} = 1$ indicates a converged result \cite{gelman+rubin1992}. We also performed visual checks of the sampled chains on all hyperparameters and of the best-fit model compared to both the raw and smoothed asteroseismic data. We found no issues in the visual investigation of the 94 stars. KIC 8478994 was excluded due to both a poor fit as well as high $\hat{R}$ on rotational parameters. KICs 6603624, 8760414 and 8938364 are reported in \textbf{Extended Data} Table 1, but were excluded from the gyrochronology analysis due to strong disagreement with multiple studies in the literature (see main body of paper). Finally, we flagged any stars with fewer than 1000 effective samples ($n_{\rm eff}$) of $\nu_s$.

\section{Gyrochronology Methods}\label{s:gyro}
\subsection{Stellar Models}\label{ssec:models}
The braking models used in this work have several parameters that inform the rotational evolution. These are: a normalization factor to reproduce the solar rotation ($f_k$); a disk locking timescale ($T_{\rm disk}$) and period ($P_{\rm disk}$) which together regulate the stellar angular velocity during the pre-main sequence; the critical angular velocity that marks the transition from saturated (rapidly rotating) to unsaturated (slowly rotating) regimes ($\omega_{\rm crit}$), and the critical Rossby number, above which stars conserve angular momentum ($Ro_{\rm crit}$), mentioned above. $T_{\rm disk}$, $P_{\rm disk}$ and $\omega_{\rm crit}$ are calibrated to match the behavior in young open clusters, but have little impact on the rotational evolution beyond $\approx 1\, \rm{Gyr}$ in solar-mass stars. Both $f_k$ and $Ro_{\rm crit}$ affect the late-time evolution. Both models adopt $\omega_{\rm crit} = 3.4  \times 10^{-5}\, \rm{s}^{-1}$, $P_{\rm disk} = 8.1$, $T_{\rm disk} = 0.28$ and $f_k = 6.6$. In the weakened magnetic braking model, $Ro_{\rm crit} = 1.97$. For further details, see \cite{vansaders+pinsonneault2013} and \cite{vansaders+2016, vansaders+2019} for the standard and weakened magnetic braking cases respectively.

To construct a synthetic population of rotating stars, we expanded upon previous forward-models of the \textit{Kepler} field with the purpose of studying weakened magnetic braking \cite{vansaders+2019}, with some important improvements. We started with a TRILEGAL \cite{girardi+2012} Milky-Way simulation of the \kepler field, using the simulation's standard population values intended for this purpose. In order to replicate the \kepler selection effect, the TRILEGAL simulation was matched to the largest current catalogue of temperatures, luminosities and 2MASS $K$-band magnitudes of stars in the \kepler field \cite{berger+2020}. This was done using a nearest-neighbours approach, based on the density of stars on the HR diagram. This ensured that the TRILEGAL population matched the density of stars actually observed by \kepler, replicating its selection effects, and improved upon previous efforts \cite{vansaders+2019} by incorporating contemporary \textit{Gaia} mission data \cite{gaiacollaboration+2018}.

We made further changes to account for possible binarity in the the matching sample \cite{berger+2020}. If the first step is performed blindly, blended binaries in the sample cause an overestimation of the number of old stars. In order to overcome this, we:

\begin{enumerate}
	\item blended the TRILEGAL stars with binary companions drawn from a flat mass-ratio distribution, using a known binary fraction \cite{raghavan+2010},
	\item recalculated the `observed' luminosities and magnitudes assuming that each binary pair was blended, and
	\item shifted these stars' temperatures following a $g$-$K$ magnitude relation \cite{berger+2020}.
\end{enumerate}

@@

Our asteroseismic sample of stars with short cadence observations are subject to additional selection functions not included in the creation of the model populations above. We did \textit{not} explicitly account for these asteroseismic selection functions in our model, by design. Both the standard and WMB models contain stars with the same fundamental parameters (mass, radius, effective temperature, metallicity) but a different period based on the choice of rotational evolution prescription. Applying an asteroseismic selection function that depends on these fundamental parameters would apply an identical prior to both models, therefore providing no net effect on our posterior distribution \cite{chaplin+2011}.  Additionally, we expected any seismic selection function to be relatively flat (and therefore uninformative) on a star-by-star scale, on which we run our model analysis.

\subsection{Bayesian Mixture Model}
In order to determine whether weakened magnetic braking occurs on the main sequence, we compared our sample of seismic age and rotation, along with temperature, metallicity and mass, to the two stellar population models of the \kepler field adapted from \cite{vansaders+2019}, discussed above. Both stellar models were evaluated in a Bayesian framework, with the rationale of determining which of the two models (standard or WMB) is most likely to reproduce our observed data. Each model sample contained temperature (\teff), mass ($M$), age ($t$), metallicity ($\rm{[Fe/H]}$) and rotation ($P$) information.

In order to draw probabilistic inference about the models, we built a five-dimensional Kernel Density Estimate (KDE) of both model populations using the \texttt{statsmodels} package \cite{seabold+perktold2010}. We used a band-width (setting the resolution of the KDE) of $0.02\, M_\odot$ in mass, $10\, \rm K$ in \teff, $0.01\, \rm{dex}$ in $\ln(t)$, $0.01\, \rm{dex}$ in $\rm{[Fe/H]}$ and $0.01\, \rm{dex}$ in $\ln(P)$. Note that age and rotation were treated in log space, where the posterior estimates from asteroseismology more closely resemble normal distributions. This approach translates the population models to a probability distribution we can use in a Bayesian framework.

@@

The final term, $p(P_{\rm s})$, represents the prior on the mixture model weight, which is uniform between 0 and 1. A visual representation of our model is shown in Figure \ref{fig:pgm}.

Typically, this model would evaluate all stars in our sample against the stellar models simultaneously for a single posterior estimate of $P_{\rm s}$. At 95 stars, in 5 parameter spaces, this totals 476 free parameters to marginalise over. This is not an issue for Hamiltonian Monte Carlo \cite[HMC]{betancourt+girolami2013}, however the use of KDE functions, over which a probabilistic gradient can not be measured, reduces HMCs effectiveness. Alternative Markov Chain Monte Carlo techniques \cite[MCMC]{foreman-mackey+2013} can more efficiently sample the KDE functions, but can not treat the large number of hierarchical parameters. To overcome this, we fit our model to each star to obtain an independent individual posterior distribution for $P_{\rm s}$, and multiplied these post hoc to obtain a combined posterior. This comes with the benefit of easily allowing us to calculate the combined posterior for different stellar classifications, at the expense of the ability to marginalise for a single value of $P_{\rm s}$ directly.\\

@@

We fit our model Equation \ref{eq:modelll} using \texttt{emcee} \cite{foreman-mackey+2013, foreman-mackey2016}, using 32 walkers for a total of 7500 samples per walker, of which the first 2500 were discarded as a burn-in.

@@

We also compared our asteroseismic estimates of stellar rotation with similar studies in the literature, shown in \textbf{Extended Data} Figure \ref{fig:literaturecomp}. These included: a study of the binary solar analogues 16 Cyg A \& B \cite{davies+2015}, ; a study of surface and seismic rotation which our catalogue shares 5 stars with \cite{nielsen+2015}, ; and an asteroseismic study of differential rotation with which our catalogue shares 40 targets \cite{benomar+2018}. For the latter, we used their reported splitting value $a_1$, which is equivalent to $\nu_{\rm s}$.

Overall,  \textbf{Extended Data} Figure \ref{fig:literaturecomp} shows no strong disagreements between our asteroseismic measurements for stellar rotation and those from the literature. The scatter of the fractional differences lies cleanly around the zero line, with a mean and spread of $0.0_{-15.6}^{+16.4}\, \%$. The increase in uncertainty with period is due to more slowly rotating stars being more difficult to constrain using asteroseismology.
% The agreement within $1\sigma$ here is encouraging, indicating that these independent Bayesian analyses are finding appropriate uncertainties on these rotation measurements.

It is of note that 16 Cyg A was found to be rotating slightly faster in our analysis compared to the literature \cite{davies+2015} (deviating within $2\sigma$), despite the fit being performed on the same data. We found an inclination angle that is slightly lower for 16 Cyg A but at a similar projected splitting, which would explain finding a lower value of rotation.

@@

\subsection{Seismic vs spectroscopic rotation}
A distinct difference between rotation rates obtained through different techniques may hold information about differential rotation (both latitudinal and radial) of near-surface layers, such as those we observe in the Sun \cite{beck2000}.  A previous comparison of spectroscopic and seismic rotation rates, performed on a sample of 22 stars, found no significant radial differential rotation \cite{benomar+2018}. In this work they not only considered rotation rates from spots, but also spectroscopic measures of the projected surface rotation $\textrm{v}\sin(i)$, which they found to be more reliable.

With our expanded sample of asteroseismic rotation we can perform a similar analysis, to both validate our sample and probe radial differential rotation.  \textbf{Extended Data} Figure \ref{fig:vsinilit} shows a comparison between spectroscopic $\textrm{v}\sin(i)$ measurements as listed in LEGACY and `Kages' (left) and \cite{benomar+2015} (right). In these cases the asteroseismic $\textrm{v}\sin(i)$ has been calculated using our measure of asteroseismic $\nu_s\sin(i)$ and the known asteroseismic radii. Three stars (KICs 6603624, 8760414 and 8938364) have been excluded from this figure due to strong disagreements of measured rotation rates with the literature (see above).

For the LEGACY and `Kages' sample, we find no strong deviation from the 1:1 line except at very low velocities, which is likely due to biases inherent to spectroscopic line broadening measurements \cite{doyle+2014, tayar+2015}. For the \cite{benomar+2015} sample stars lie a lot closer to the 1:1 line.

Overall, there appears to be a global offset where spectroscopic measurements of projected rotation appear faster than asteroseismic measures. Based on the LEGACY and `Kages' $v\sin(i)$ values, this offset is roughly $18\%$ (i.e. spectroscopic projected rotation rates are faster than asteroseismic rates). This offset is much smaller ($\sim5\%$) for the \cite{benomar+2015} sample, albeit for far fewer stars. These offsets are within the typical disagreement between spectroscopic methods, based on comparisons of projected rotation measurements for red giant stars \cite[see Figure 2]{tayar+2015}, especially at $< 5\, \rm{km\,s^{-1}}$.

@@

\begin{itemize}
	\item \textit{Fast rotating stars:} In prinicple, a star could rotate fast enough that the highest-frequency peak in a split dipole ($\ell = 2$) mode would overlap with the radial ($\ell = 0$) mode. This would occur if $2\nu_{\rm s}$ > $\delta\nu_{02}$, the small separation. For the star in our sample with the smallest $\delta\nu_{02}$ (so the highest risk of this happening), this would occur at a rotation of 8.8 days or faster. For the star with the largest $\delta\nu_{02}$, this limit was roughly 2 days.

@@

Finally, we also consider bias in asteroseismic detections. The probability of an asteroseismic detection with \kepler scales with temperature and radius (i.e. scales inversely with \logg, and therefore main sequence age) \cite{chaplin+2011, schofield+2019}. More active, magnetic stars may also suppress their oscillation modes, making it more likely to detect seismic oscillations in older stars \cite{mathur+2019}. Through these two effects, asteroseismology is biased towards detecting older over younger stars. As it is older stars, undergoing magnetic braking, that are required to drive the distinction between stellar models, we do not expect this observing bias to effect our conclusions.

\section{Verifying consequences for gyrochronology}
\subsection{Limits of our stellar models}\label{ssec:limits}
The rotational stellar models used in this work \cite{vansaders+2019} are constructed for metallicities of $-0.4 < \rm{[Fe/H]} < 0.4\, \rm{dex}$, in steps of $0.1\, \rm {dex}$. Our sample of 91 stars contained 4 stars with metallicities below $-0.4\, \rm{dex}$, which are shown as shaded symbols in Figure \ref{fig:fullsample}. Of these, 3 were included in our final sample of 73 stars used to evaluate our stellar models: KICs 7970740, 8684723 and KIC 9965715. All three are classed as MS stars, with metallicities of $-0.54 \pm 0.10$, $-0.42 \pm 0.10$ and $-0.44 \pm 0.18\, \rm {dex}$ respectively, placing them within $3\sigma$ of the metallicity limits of our stellar models. KICs 8684723 and 9965715 strongly agree with the WMB model, whereas KIC 7970740 weakly prefers the standard model. Excluding these stars was not found to significantly alter the joint posterior distribution shown in Figure \ref{fig:gyroresults}.

>>>>

%\documentclass[12pt]{article}
%\setlength{\textwidth}{167mm}
%\setlength{\headsep}{0mm}
%\setlength{\headheight}{0mm}
%\setlength{\textheight}{230mm}
%\setlength{\oddsidemargin}{1.6mm}
%\setlength{\evensidemargin}{1.6mm}
%\setlength{\topmargin}{4.6mm}
%
%\usepackage{chngcntr}
%\usepackage{xspace}
%\usepackage{graphicx}
%\usepackage{amsmath}	% Advanced maths commands
%\usepackage{amssymb}	% Extra maths symbols
%\usepackage[ ]{hyperref}
%\graphicspath{{Images/}}
%%\usepackage[symbol]{footmisc}
%
%
%% Astronomical abbreviations (thanks to Dan Huber)
%\newcommand{\numax}{\mbox{$\nu_{\rm max}$}\xspace}
%\newcommand{\dnu}{\mbox{$\Delta \nu$}\xspace}
%\newcommand{\muHz}{\mbox{$\mu$Hz}\xspace}
%\newcommand{\teff}{\mbox{$T_{\rm eff}$}\xspace}
%\newcommand{\logg}{\mbox{$\log(g)$}\xspace}
%\newcommand{\feh}{\mbox{$\rm{[Fe/H]}$}\xspace}
%\newcommand{\msun}{\mbox{$\mathrm{M}_{\odot}$}\xspace}
%\newcommand{\lsun}{\mbox{$\mathrm{L}_{\odot}$}\xspace}
%\newcommand{\mearth}{\mbox{$\mathrm{M}_{\oplus}$}\xspace}
%\newcommand{\rsun}{\mbox{$\mathrm{R}_{\odot}$}\xspace}
%\newcommand{\kepler}{\emph{Kepler}\xspace}
%\newcommand{\tess}{\emph{TESS}\xspace}
%\newcommand{\ktwo}{K2\xspace}
%\newcommand{\gaia}{\emph{Gaia}\xspace}
%
%\begin{document}

\section*{\underline{Methods}}
\setcounter{tocdepth}{2}
\tableofcontents
\section{Asteroseismic Methods}
\subsection{Asteroseismic Data}
For our asteroseismic power spectrum data we used the unweighted power spectra from the KASOC pipeline \cite{m_handberg+lund2014}\footnote{Obtainable from the \href{http://kasoc.phys.au.dk/}{KASOC} webpage.}. We did not apply any additional treatment to these data. For 16 Cyg A \& B (KIC 12069424 and KIC 12069449) we used the KEPSEISMIC lightcurves \cite{m_garcia+2011}\footnote{Obtainable from \href{https://archive.
		stsci.edu/prepds/kepseismic/}{MAST}.}, which have significantly better signal-to-noise for these two stars.

For our asteroseismic ages, we used the ages obtained by \texttt{BASTA} \cite[BAyesian STellar Algorithm]{m_silvaaguirre+2015} in the `Kages' and LEGACY catalogues. These ages have been obtained by comparisons of measured oscillation properties to stellar models, accounting for an expanded range of metallicities. \texttt{BASTA} is thoroughly compared to four other seismic modelling techniques in \cite{m_silvaaguirre+2017}. While uncertainties found through \texttt{BASTA} are typically higher than for other techniques, only \texttt{BASTA} and \texttt{ASTFIT} \cite[Aarhus STellar Evolution Code]{m_christensen-dalsgaard2008} recover the radius, mass and age of the Sun, when applied to solar data. Although the uncertainties on \texttt{ASTFIT} ages are overall lower, they are not published for the `Kages' sample. In order to maintain an internally consistent stellar age sample, we used age results from \texttt{BASTA} for both the `Kages' and LEGACY samples.

@@

As described in the catalogue papers, for `Kages' stars atmospheric properties (\teff and \feh) were measured through high-resolution spectroscopy \cite{m_huber+2013a}. For LEGACY stars, atmospheric properties were similarly taken from one study \cite{m_buchhave+latham2015} for most stars in the catalogue, and complemented by other values from the literature for the remaining stars \cite[see Table 3]{m_silvaaguirre+2017}.

Other asteroseismic properties used in this study, such as those used as first guesses on the free parameters in our asteroseismic model, were taken from the `Kages' and LEGACY catalogues \cite{m_astropycollaboration+2013, m_astropycollaboration+2018, m_ginsburg+2019}. In cases where both catalogues contained the same target, we used the stellar parameters reported in LEGACY \cite{m_mckinney2010}. This is also the case for the masses and ages described above.

@@

In order to extract signatures of stellar rotation from the asteroseismic mode frequencies, we built a model that simultaneously treats the convective background, modes of oscillation, and white noise, while accounting for rotational splitting. The foundations of this approach follows best-practices in asteroseismology \cite{m_davies+2015}, fitting Harvey profiles for the background \cite{m_harvey1985}, and expressing the frequencies of the modes using an asymptotic expression \cite{m_tassoul1980, m_vrard+2016}.

The first core improvement in this work come in the form of the use of hierarchical latent variable models \cite{m_hogg+2010, m_hall+2019}, which account for small-scale deviations in mode frequencies due to effects not explicitly accounted for in our model (such as acoustic glitches \cite{m_mazumdar+2014}). By improving the inference of mode frequencies in this way, we also improve the ability to resolve the rotational splitting. The second improvement comes in the form of priors on our parameters, and in particular the rotational inclination, which more accurately reflects the true distribution of angles than previous techniques \cite{m_chaplin+basu2017}. A step-by-step breakdown of the model and all priors can be found in \textbf{Supplementary Materials}.\\

We separated our model fitting into two parts. First, we fit a model for the convective background and white noise only, to the region of the power spectra that did not contain modes of oscillation. This was done using \texttt{PyStan} \cite{m_vanhoey+2013, m_carpenter+2017}, for 10,000 iterations on each star\footnote{These \texttt{PyStan} runs were initiated with a random seed of 11, as were all other random processes in this work}. Second, we fit our full model (including the convective background) to the region containing the modes of oscillation. The results of the first fit to the convective background were used as extremely informative priors on the background parameters in this second fit. This was done using \texttt{PyMC3} \cite{m_vanderwalt+2011,m_salvatier+2016, m_thetheanodevelopmentteam+2016} for 2500 iterations each on 4 chains.

From this asteroseismic analysis, we report inclination angle ($i$), rotational splitting ($\nu_{\rm s}$), and rotation period ($P$) in \textbf{Extended Data} Table \ref{tab:results}. The summary statistics on these parameters were taken as the median of the posterior distribution, with uncertainties being the $15.9^{\rm th}$ and $84.1^{\rm st}$ percentiles. For inclination angle ($i = \arccos(\cos(i))$) and rotation ($P = 1/\nu_{\rm s}$), the full posterior samples were transformed before taking the summary statistics, as our model sampled in $\cos(i)$ and $\nu_{\rm s}$.

We flagged any sub-optimal conditions of the final fit. Of 94 stars, we flagged 5 for which the Gelman-Rubin convergence metric, $\hat{R}$, was greater than 1.01 and 2 stars for which it was greater than 1.1 on inclination angle or rotation, where a $\hat{R} = 1$ indicates a converged result \cite{m_gelman+rubin1992}. We also performed visual checks of the sampled chains on all hyperparameters and of the best-fit model compared to both the raw and smoothed asteroseismic data. We found no issues in the visual investigation of the 94 stars. KIC 8478994 was excluded due to both a poor fit as well as high $\hat{R}$ on rotational parameters. KICs 6603624, 8760414 and 8938364 are reported in \textbf{Extended Data} Table \ref{tab:results}, but were excluded from the gyrochronology analysis due to strong disagreement with multiple studies in the literature (see main body of paper). Finally, we flagged any stars with fewer than 1000 effective samples ($n_{\rm eff}$) of $\nu_s$.

\section{Gyrochronology Methods}\label{s:gyro}
\subsection{Stellar Models}\label{ssec:models}
The braking models used in this work have several parameters that inform the rotational evolution. These are: a normalization factor to reproduce the solar rotation ($f_k$); a disk locking timescale ($T_{\rm disk}$) and period ($P_{\rm disk}$) which together regulate the stellar angular velocity during the pre-main sequence; the critical angular velocity that marks the transition from saturated (rapidly rotating) to unsaturated (slowly rotating) regimes ($\omega_{\rm crit}$), and the critical Rossby number, above which stars conserve angular momentum ($Ro_{\rm crit}$), mentioned above. $T_{\rm disk}$, $P_{\rm disk}$ and $\omega_{\rm crit}$ are calibrated to match the behavior in young open clusters, but have little impact on the rotational evolution beyond $\approx 1\, \rm{Gyr}$ in solar-mass stars. Both $f_k$ and $Ro_{\rm crit}$ affect the late-time evolution. Both models adopt $\omega_{\rm crit} = 3.4  \times 10^{-5}\, \rm{s}^{-1}$, $P_{\rm disk} = 8.1$, $T_{\rm disk} = 0.28$ and $f_k = 6.6$. In the weakened magnetic braking model, $Ro_{\rm crit} = 1.97$. For further details, see \cite{m_vansaders+pinsonneault2013} and \cite{m_vansaders+2016, m_vansaders+2019} for the standard and weakened magnetic braking cases respectively.

To construct a synthetic population of rotating stars, we expanded upon previous forward-models of the \textit{Kepler} field with the purpose of studying weakened magnetic braking \cite{m_vansaders+2019}, with some important improvements. We started with a TRILEGAL \cite{m_girardi+2012} Milky-Way simulation of the \kepler field, using the simulation's standard population values intended for this purpose. In order to replicate the \kepler selection effect, the TRILEGAL simulation was matched to the largest current catalogue of temperatures, luminosities and 2MASS $K$-band magnitudes of stars in the \kepler field \cite{m_berger+2020}. This was done using a nearest-neighbours approach, based on the density of stars on the HR diagram. This ensured that the TRILEGAL population matched the density of stars actually observed by \kepler, replicating its selection effects, and improved upon previous efforts \cite{m_vansaders+2019} by incorporating contemporary \textit{Gaia} mission data \cite{m_gaiacollaboration+2018}.

We made further changes to account for possible binarity in the the matching sample \cite{m_berger+2020}. If the first step is performed blindly, blended binaries in the sample cause an overestimation of the number of old stars. In order to overcome this, we:

\begin{enumerate}
	\item blended the TRILEGAL stars with binary companions drawn from a flat mass-ratio distribution, using a known binary fraction \cite{m_raghavan+2010},
	\item recalculated the `observed' luminosities and magnitudes assuming that each binary pair was blended, and
	\item shifted these stars' temperatures following a $g$-$K$ magnitude relation \cite{m_berger+2020}.
\end{enumerate}

@@

Our asteroseismic sample of stars with short cadence observations are subject to additional selection functions not included in the creation of the model populations above. We did \textit{not} explicitly account for these asteroseismic selection functions in our model, by design. Both the standard and WMB models contain stars with the same fundamental parameters (mass, radius, effective temperature, metallicity) but a different period based on the choice of rotational evolution prescription. Applying an asteroseismic selection function that depends on these fundamental parameters would apply an identical prior to both models, therefore providing no net effect on our posterior distribution \cite{m_chaplin+2011}.  Additionally, we expected any seismic selection function to be relatively flat (and therefore uninformative) on a star-by-star scale, on which we run our model analysis.

\subsection{Bayesian Mixture Model}
In order to determine whether weakened magnetic braking occurs on the main sequence, we compared our sample of seismic age and rotation, along with temperature, metallicity and mass, to the two stellar population models of the \kepler field \cite{m_vansaders+2019}, discussed above. Both stellar models were evaluated in a Bayesian framework, with the rationale of determining which of the two models (standard or WMB) is most likely to reproduce our observed data. Each model sample contained temperature (\teff), mass ($M$), age ($t$), metallicity ($\rm{[Fe/H]}$) and rotation ($P$) information.

In order to draw probabilistic inference about the models, we built a five-dimensional Kernel Density Estimate (KDE) of both model populations using the \texttt{statsmodels} package \cite{m_seabold+perktold2010}. We used a band-width (setting the resolution of the KDE) of $0.02\, M_\odot$ in mass, $10\, \rm K$ in \teff, $0.01\, \rm{dex}$ in $\ln(t)$, $0.01\, \rm{dex}$ in $\rm{[Fe/H]}$ and $0.01\, \rm{dex}$ in $\ln(P)$. Note that age and rotation were treated in log space, where the posterior estimates from asteroseismology more closely resemble normal distributions. This approach translates the population models to a probability distribution we can use in a Bayesian framework.

@@

The final term, $p(P_{\rm s})$, represents the prior on the mixture model weight, which is uniform between 0 and 1. A visual representation of our model is shown in \textbf{Extended Data} Figure \ref{fig:pgm}.

Typically, this model would evaluate all stars in our sample against the stellar models simultaneously for a single posterior estimate of $P_{\rm s}$. At 95 stars, in 5 parameter spaces, this totals 476 free parameters to marginalise over. This is not an issue for Hamiltonian Monte Carlo \cite[HMC]{m_betancourt+girolami2013}, however the use of KDE functions, over which a probabilistic gradient can not be measured, reduces HMCs effectiveness. Alternative Markov Chain Monte Carlo techniques \cite[MCMC]{m_foreman-mackey+2013} can more efficiently sample the KDE functions, but can not treat the large number of hierarchical parameters. To overcome this, we fit our model to each star to obtain an independent individual posterior distribution for $P_{\rm s}$, and multiplied these post hoc to obtain a combined posterior. This comes with the benefit of easily allowing us to calculate the combined posterior for different stellar classifications, at the expense of the ability to marginalise for a single value of $P_{\rm s}$ directly.\\

@@

We fit our model Equation \ref{eq:modelll} using \texttt{emcee} \cite{m_foreman-mackey+2013, m_foreman-mackey2016}, using 32 walkers for a total of 7500 samples per walker, of which the first 2500 were discarded as a burn-in.

@@

We also compared our asteroseismic estimates of stellar rotation with similar studies in the literature, shown in \textbf{Extended Data} Figure \ref{fig:literaturecomp}. These included: a study of the binary solar analogues 16 Cyg A \& B \cite{m_davies+2015}, ; a study of surface and seismic rotation which our catalogue shares 5 stars with \cite{m_nielsen+2015}, ; and an asteroseismic study of differential rotation with which our catalogue shares 40 targets \cite{m_benomar+2018}. For the latter, we used their reported splitting value $a_1$, which is equivalent to $\nu_{\rm s}$.

Overall,  \textbf{Extended Data} Figure \ref{fig:literaturecomp} shows no strong disagreements between our asteroseismic measurements for stellar rotation and those from the literature. The scatter of the fractional differences lies cleanly around the zero line, with a mean and spread of $0.0_{-15.6}^{+16.4}\, \%$. The increase in uncertainty with period is due to more slowly rotating stars being more difficult to constrain using asteroseismology.

It is of note that 16 Cyg A was found to be rotating slightly faster in our analysis compared to the literature \cite{m_davies+2015} (deviating within $2\sigma$), despite the fit being performed on the same data. We found an inclination angle that is slightly lower for 16 Cyg A but at a similar projected splitting, which would explain finding a lower value of rotation.

@@

\subsection{Seismic vs spectroscopic rotation}
A distinct difference between rotation rates obtained through different techniques may hold information about differential rotation (both latitudinal and radial) of near-surface layers, such as those we observe in the Sun \cite{m_beck2000}.  A previous comparison of spectroscopic and seismic rotation rates, performed on a sample of 22 stars, found no significant radial differential rotation \cite{m_benomar+2018}. In this work they not only considered rotation rates from spots, but also spectroscopic measures of the projected surface rotation $\textrm{v}\sin(i)$, which they found to be more reliable.

With our expanded sample of asteroseismic rotation we can perform a similar analysis, to both validate our sample and probe radial differential rotation.  \textbf{Extended Data} Figure \ref{fig:vsinilit} shows a comparison between spectroscopic $\textrm{v}\sin(i)$ measurements as listed in LEGACY and `Kages' (left) and Benomar et al. (2015) \cite{m_benomar+2015} (right). In these cases the asteroseismic $\textrm{v}\sin(i)$ has been calculated using our measure of asteroseismic $\nu_s\sin(i)$ and the known asteroseismic radii. Three stars (KICs 6603624, 8760414 and 8938364) have been excluded from this figure due to strong disagreements of measured rotation rates with the literature (see above).

For the LEGACY and `Kages' sample, we find no strong deviation from the 1:1 line except at very low velocities, which is likely due to biases inherent to spectroscopic line broadening measurements \cite{m_doyle+2014, m_tayar+2015}. For the Benomar et al. (2015) sample stars lie a lot closer to the 1:1 line.

Overall, there appears to be a global offset where spectroscopic measurements of projected rotation appear faster than asteroseismic measures. Based on the LEGACY and `Kages' $v\sin(i)$ values, this offset is roughly $18\%$ (i.e. spectroscopic projected rotation rates are faster than asteroseismic rates). This offset is much smaller ($\sim5\%$) for the \cite{m_benomar+2015} sample, albeit for far fewer stars. These offsets are within the typical disagreement between spectroscopic methods, based on comparisons of projected rotation measurements for red giant stars \cite[see Figure 2]{m_tayar+2015}, especially at $< 5\, \rm{km\,s^{-1}}$.

@@

\begin{itemize}
	\item \textit{Fast rotating stars:} In prinicple, a star could rotate fast enough that the highest-frequency peak in a split dipole ($\ell = 2$) mode would overlap with the radial ($\ell = 0$) mode. This would occur if $2\nu_{\rm s} > \delta\nu_{02}$, the small separation. For the star in our sample with the smallest $\delta\nu_{02}$ (so the highest risk of this happening), this would occur at a rotation of 8.8 days or faster. For the star with the largest $\delta\nu_{02}$, this limit was roughly 2 days.

@@

Finally, we also consider bias in asteroseismic detections. The probability of an asteroseismic detection with \kepler scales with temperature and radius (i.e. scales inversely with \logg, and therefore main sequence age) \cite{m_chaplin+2011, m_schofield+2019}. More active, magnetic stars may also suppress their oscillation modes, making it more likely to detect seismic oscillations in older stars \cite{m_mathur+2019}. Through these two effects, asteroseismology is biased towards detecting older over younger stars. As it is older stars, undergoing magnetic braking, that are required to drive the distinction between stellar models, we do not expect this observing bias to effect our conclusions.

\section{Verifying consequences for gyrochronology}
\subsection{Limits of our stellar models}\label{ssec:limits}
The rotational stellar models used in this work \cite{m_vansaders+2019} are constructed for metallicities of $-0.4 < \rm{[Fe/H]} < 0.4\, \rm{dex}$, in steps of $0.1\, \rm {dex}$. Our sample of 91 stars contained 4 stars with metallicities below $-0.4\, \rm{dex}$, which are shown as shaded symbols in Figure \ref{fig:fullsample}. Of these, 3 were included in our final sample of 73 stars used to evaluate our stellar models: KICs 7970740, 8684723 and KIC 9965715. All three are classed as MS stars, with metallicities of $-0.54 \pm 0.10$, $-0.42 \pm 0.10$ and $-0.44 \pm 0.18\, \rm {dex}$ respectively, placing them within $3\sigma$ of the metallicity limits of our stellar models. KICs 8684723 and 9965715 strongly agree with the WMB model, whereas KIC 7970740 weakly prefers the standard model. Excluding these stars was not found to significantly alter the joint posterior distribution shown in Figure \ref{fig:gyroresults}.
